Dashboards for stock assessments: Getting started

### 2019-10-18 analysis/dashboards/getting_started.Rmd
Draft a flexdashboard basics page to the getting_started dashboard

- Uses [**rmarkdown**](https://rmarkdown.rstudio.com/) to render a group of related figures, tables and text into a dashboard  
- Layout is flexible and the components automatically re-size to fill the browser and adapt to mobile displays
- Supports a wide range of components, including base plot, ggplots, gauges, tables and [htmlwidgets](http://www.htmlwidgets.org/index.html) such as [**plotly**](https://plotly-r.com)
- Optionally use [**shiny**](http://shiny.rstudio.com/) or [**crosstalk**](https://rstudio.github.io/crosstalk/) to bolster interactivity

@@

- Enables cross-widget interactions by linking brushing and/or filtering across multiple views
- i.e. Interactions with one plot can affect change in another plot  
- Supports a wide range of [htmlwidgets](http://www.htmlwidgets.org/index.html), such as [**plotly**](https://plotly-r.com) and [**leaflet**](https://rstudio.github.io/leaflet/)

@@

Finally, mix in `R` code by surrounding chunks of code using one backtick for inline code (e.g.`` `r knitr::inline_expr("1+1")` `` will print 2 in the output) or three backticks to run several lines of code and/or display a table or plot. The below chunk will print the top three rows of the `cars` data-set:

@@

>>>>

- Uses [**rmarkdown**](https://rmarkdown.rstudio.com/) to render a group of related figures, tables and text into a dashboard  
- Layout is flexible and the components automatically re-size to fill the browser and adapt to mobile displays
- Supports a wide range of components, including base plot, ggplots, gauges, tables and [htmlwidgets](http://www.htmlwidgets.org/index.html) such as [**plotly**](https://plotly-r.com), [**leaflet**](https://rstudio.github.io/leaflet/) and [**DT**](https://rstudio.github.io/DT/)
- Optionally use [**shiny**](http://shiny.rstudio.com/) or [**crosstalk**](https://rstudio.github.io/crosstalk/) to bolster interactivity

@@

- Enables cross-widget interactions by linking brushing and/or filtering across multiple views
- i.e. Interactions with one plot can affect change in another plot  
- Supports a wide range of [htmlwidgets](http://www.htmlwidgets.org/index.html), such as [**plotly**](https://plotly-r.com), [**leaflet**](https://rstudio.github.io/leaflet/) and [**DT**](https://rstudio.github.io/DT/)

@@

Finally, mix in `R` code by surrounding chunks of code using one backtick for inline code (e.g.`` `r knitr::inline_expr("1+1")` `` will print 2 in the output) or three backticks to run several lines of code and/or display a table or plot. The chunk below will print the top three rows of the `cars` data-set:

@@

flexdashboard {data-navmenu="Basics"}
=======================================================================

Row {data-height=200}
-------------------------------------

The `flexdashboard` package can be used to render groups of related text, figures and tables into a dashboard. Using a combination of `markdown` syntax and `R` code (i.e. R markdown), this package facilitates a wide range of layout options and each component can include output from packages such as `plotly`, `leaflet`, `ggplot2`, and so on. The package also integrates nicely with `shiny` and `crosstalk`, providing options for increasing the interactivity of the dashboard. Some layout and component options are highlited below.

### Layout

Individual charts are defined using markdown's level 3 header (`### Chart title`) and they are, by default, stacked vertically within columns defined using markdown's level 2 header (`---------`). The code below will create a `flexdashboard` with two stacked columns and three charts:

````
---
title: "Layout example 1"
output: flexdashboard::flex_dashboard
---

Column
-------------------------------------

### Chart 1

Column
-------------------------------------

### Chart 2

### Chart 3

The output from this example has been duplicated [here](#layout-example-1).

Alternatively, charts can be organized by row by modifying the YAML header:

````
---
title: "Layout example 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

Row
-------------------------------------

### Chart 1

Row
-------------------------------------

### Chart 2

### Chart 3

````
The output from this example has been duplicated [here](#layout-example-2).

### Components

The components of a dashboard can hold a wide range of outputs. The code below generates a mixture of tabular and graphical output. The table is generated following `markdown` syntax with inline `R` code and the interactive plot is generated using `plotly`.

````
---
title: "Components example"
output: flexdashboard::flex_dashboard
---

Column {data-width=300}
-------------------------------------

### Table

Summary statistics of the `volcano` data-set

| Statistic     | Elevation                   |
|:------------- |:--------------------------- |
| Min           | `r knitr::inline_expr('min(volcano)')`            | 
| Median        | `r knitr::inline_expr('median(volcano)')`         |
| Mean          | `r knitr::inline_expr('round(mean(volcano))')`    |
| Max           | `r knitr::inline_expr('max(volcano)')`            |

Column {data-width=700}
-------------------------------------

### Plot

```{r} `r ''`
plotly::plot_ly(z = volcano, type = "surface")
```

The output from this example has been duplicated [here](#components-example). Note the use of the `data-width` attribute to make the table chart relatively narrow.

Layout example 1 {data-orientation=columns .hidden}
=======================================================================

Column
-------------------------------------

### Chart 1

Column
-------------------------------------

### Chart 2

### Chart 3

Layout example 2 {data-orientation=rows .hidden}
=======================================================================

Row
-------------------------------------

### Chart 1

Row
-------------------------------------

### Chart 2

### Chart 3

Components example {data-orientation=columns .hidden}
=======================================================================

Column {data-width=300}
-------------------------------------

### Table

Summary statistics of the `volcano` data-set

| Statistic     | Elevation                   |
|:------------- |:--------------------------- |
| Min           | `r min(volcano)`            |
| Median        | `r median(volcano)`         |
| Mean          | `r round(mean(volcano))`    |
| Max           | `r max(volcano)`            |

Column {data-width=700}
-------------------------------------

### Plot

```{r}
plotly::plot_ly(z = volcano, type = "surface")
```
